Supplementary Information

### 2020-11-25 doc/manuscript/MEE_manuscript_SI.Rmd
Update MEE_manuscript_SI.Rmd

Our analysis included two sites where climate change has had pronounced effects on tree growth: Scotty Creek, NW Territories, Canada (SC) and Little Tesuque, New Mexico, USA (LT).
At SC, [temperatures have increased by X $^\circ$ over X years]..., resulting in negative growth trends in basal area index ($BAI$) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees [@sniderhan_growth_2016].
At LT, *(drought has increased dramatically)*, resulting in many missing rings in recent years.

>>>>

Our analysis included two sites where climate change has had pronounced effects on tree growth: Scotty Creek, NW Territories, Canada (SC) and Little Tesuque, New Mexico, USA (LT).
At SC, rapidly rising temperatures are causing melting permafrost, summer moisture stress, resulting in negative growth trends in basal area index ($BAI$) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees [@sniderhan_growth_2016].
At LT, increasingly warm drought has dramatically reduced growth [@williams_temperature_2012], resulting in many missing rings in recent years.

Problematically, correlating tree growth residuals from which climate-driven trends had been removed against the climate signal with a strong directional trend would not necessarily identify the most relevant climate drivers.

For these sites, we experimented with three approaches to identifying the most important climate drivers (1) the method described above, (2) detrending the climate variables **(AT:prewhitening?)** prior to the climwin step, and (3) splitting analyses into decades before and after 1970 [*sensu*  @sniderhan_growth_2016] (Appendix `r changing_climate`).
